Stat 400 Project

### 2021-11-23 Stat 400 proj.Rmd
Got the function deciding if people are close enough to get infected working.

#Function for deciding if infections occured
infection_status <- function(state){

@@

  #Check to see which suceptable subjects get infected
  crucial_distance <- rexp(n=nrow(coords), 1/8)

  #For loop
}

>>>>

#Function for deciding if infections occured
infection_status <- function(state, mean_crit_dist){

@@

  #store new infection status
  new_status <- rep(NA, nrow(current_suceptable))

  #Check to see which suceptable subjects get infected
  #For loop
  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_suceptable)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])
      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance){
        new_status[j] <- 'I'
      }else{new_status[j] <- 'S'}
    }
  }
  return(new_status)
}
